What We Eval in the Shadows

### 2021-08-06 paper/main.tex
minor
change
Updating provenance

       \node [block, fill = red, draw = darkred, very thick] (download) {
         \nodename{
           \vspace{1mm}\textbf{Download}\vspace{1mm}\\
           15K Packages\\
           8K Kaggle Kernels\\
           219 Kaggle Datasets
         }
       };
       \node [below = \textsep of download]   (downloaddesc)   {\nodedesc{12 Hours}};

       \node [block, right = \nodesep of download, fill = yellow, draw = darkyellow, very thick] (extract) {
         \nodename{
           \vspace{1mm}\textbf{Extract}\vspace{1mm}\\
           240K package programs\\%, 4.6M LOC\\
           74 Kaggle kernels\\%, 13K LOC\\
           \newline
         }
       };
       \node [below = \textsep of extract]   (extractdesc)   {\nodedesc{2 Hours}};

       \node [block, right = \nodesep of extract, fill = blue, draw = darkblue, very thick] (trace) {
         \nodename{
           \vspace{1mm}\textbf{Trace}\vspace{1mm}\\
           49M eval calls \\
           14M side-effects\\
           \newline
         }
       };
       \node [below = \textsep of trace]     (tracedesc)     {\nodedesc{1 Day 12 Hours}};

       \node [block, right = \nodesep of trace, fill = green, draw = darkgreen, very thick] (analyze) {
         \nodename{
           \vspace{1mm}\textbf{Analyze}\vspace{1mm}\\
           2.8M unique eval calls\\
           22\% packages use eval\\
           \newline
         }
       };
       \node [below = \textsep of analyze]    (analyzedesc)    {\nodedesc{2 Hours}};

@@

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Usage Metrics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Where does the expression passed to \eval come from? There are various means of
creating that expression, which are associated with particular use cases. We
classify them into three categories:

>>>>

       \node [block, fill = red, draw = darkred, very thick] (download) {
         \nodename{
           \vspace{1mm}\large{\textbf{Download}}\vspace{1mm}\\
           15K Packages\\
           8K Kaggle Kernels\\
           219 Kaggle Datasets
         }
       };
       \node [below = \textsep of download]   (downloaddesc)   {\nodedesc{12 Hours}};

       \node [block, right = \nodesep of download, fill = yellow, draw = darkyellow, very thick] (extract) {
         \nodename{
           \vspace{1mm}\large{\textbf{Extract}}\vspace{1mm}\\
           240K package programs\\%, 4.6M LOC\\
           74 Kaggle kernels\\%, 13K LOC\\
           \newline
         }
       };
       \node [below = \textsep of extract]   (extractdesc)   {\nodedesc{2 Hours}};

       \node [block, right = \nodesep of extract, fill = blue, draw = darkblue, very thick] (trace) {
         \nodename{
           \vspace{1mm}\large{\textbf{Trace}}\vspace{1mm}\\
           49M eval calls \\
           14M side-effects\\
           \newline
         }
       };
       \node [below = \textsep of trace]     (tracedesc)     {\nodedesc{1 Day 12 Hours}};

       \node [block, right = \nodesep of trace, fill = green, draw = darkgreen, very thick] (analyze) {
         \nodename{
           \vspace{1mm}\large{\textbf{Analyze}}\vspace{1mm}\\
           2.8M unique eval calls\\
           22\% packages use eval\\
           \newline
         }
       };
       \node [below = \textsep of analyze]    (analyzedesc)    {\nodedesc{2 Hours}};

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Usage Metrics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Where does the expression passed to \eval come from? There are various means of
creating that expression, which are associated with particular use cases. We track the functions that build expressions or combine expressions during tracing to create a direct acyclic graph of the functions creating the expression passed to \eval. Then, we pick a \emph{representative provenance}, \ie following the left-hand side of assignments in the graph.

\NOTE{I can also put the absolute number of provenances, \ie if an expression has multiple provenances, we do not keep only the representative but also the other provenances. Also, if one site sometimes gets match.call and sometimes substitute, it is not going to be counted in either of them currently.}

 Table~\ref{tab:detailed_provenances} shows the first provenances in number of sites, for a 85\% cumulative percentage. We only track the provenance of language expressions, not of floating point or strings for instance. In that case, the provenance is shown as \c{NA}.

\begin{table}
	\begin{tabular}{|c|c|c|}
		\hline
		Provenance & \#sites & \%sites \\
		\hline
		\packageProvenanceNamea & \packageNbProvenanceSitesa & \packagePercentProvenanceSitesa \\
		\packageProvenanceNameb & \packageNbProvenanceSitesb & \packagePercentProvenanceSitesb \\
		\packageProvenanceNamec & \packageNbProvenanceSitesc & \packagePercentProvenanceSitesc \\
		\packageProvenanceNamed & \packageNbProvenanceSitesd & \packagePercentProvenanceSitesd \\
		\packageProvenanceNamee & \packageNbProvenanceSitese & \packagePercentProvenanceSitese \\
		\packageProvenanceNamef & \packageNbProvenanceSitesf & \packagePercentProvenanceSitesf \\
		\packageProvenanceNameg & \packageNbProvenanceSitesg & \packagePercentProvenanceSitesg \\
		\packageProvenanceNameh & \packageNbProvenanceSitesh & \packagePercentProvenanceSitesh \\
		\packageProvenanceNamei & \packageNbProvenanceSitesi & \packagePercentProvenanceSitesi \\
		\packageProvenanceNamej & \packageNbProvenanceSitesj & \packagePercentProvenanceSitesj \\
		\packageProvenanceNamek & \packageNbProvenanceSitesk & \packagePercentProvenanceSitesk \\
		\packageProvenanceNamel & \packageNbProvenanceSitesl & \packagePercentProvenanceSitesl \\
		\packageProvenanceNamem & \packageNbProvenanceSitesm & \packagePercentProvenanceSitesm \\
		\packageProvenanceNamen & \packageNbProvenanceSitesn & \packagePercentProvenanceSitesn \\
		\hline
	\end{tabular}
	\caption{First provenances in number of sites.} \label{tab:detailed_provenances}
\end{table}

 We
classify them into three categories:
